Data analytics effects in Baseball player's value

### 2023-12-16 manuscription/manuscription.tex
Updated Method secion by adding more content should consider

Following are definitions we may use:
\begin{table}[htbp]
  \caption{Baseball Batting Statistics}
  \label{tab:discription} 
  \centering
  \begin{tabular}{|l|l|}
     \hline
     \textbf{Variable} & \textbf{Description}\\
     \hline
     $AB$ & At bats\\
     $AVG$ & Batting average\\
     $H$ & Hits\\
     $K$ & Strikeouts\\
     $HR$ & Home Run\\
     $BABIP$ & Batting Average on Balls in Play\\
     $SF$ & Sacrifice flies\\
    \hline
  \end{tabular}
\end{table}

>>>>

Measuring playing time in baseball isn't always straightforward. At the team level, the fundamental unit is the
out, crucial for both offense and defense. Pitchers and fielders often use outs, games, or innings, but when 
it comes to batting, plate appearances or at-bats are commonly used. The challenge arises as plate appearances 
are not fixed, impacting a player's contribution.Most run estimators focus on runs per out,
emphasizing the importance of using the correct unit of playing 
time. Linear run estimators typically use plate appearances. It's crucial to recognize that comparing players 
should consider the same number of batting outs, not plate appearances.To make it more relatable, 
some analysts convert runs per out to runs per plate appearance. This simplification 
helps those more accustomed to plate appearances as the unit of playing time for hitters. The key is precision 
when comparing and evaluating player performance metrics.

In sabermetrics, it's widely accepted that a player's runs contribution should be separated from the 
impact of their home park. The debate revolves around using either simple, run-based park factors or more 
detailed component park factors.

For a value metric, the general preference is for run-based park factors. This adjustment accounts 
for the fact that the value of a run can vary based on the ballpark - for instance, a run in Coors is 
considered less valuable than a run in Petco. While there are situations where component park factors might 
be relevant, they don't necessarily provide a "more accurate" assessment of a player's value, especially 
concerning explaining team wins. The choice between the two depends on the specific analysis goals and nuances.

Fielding value is more difficult to quantify because, while there is only one hitter, the defense has nine 
fielders on every play. It is quite simple to determine who made a specific play, but it is frequently 
difficult to determine who should be liable for a ball when no play is made. Various defensive metrics attempt 
to determine who is responsible for a ball in play. In general, the better the outcomes, the more detailed the 
underlying dataset.

Table~\ref*{tab:discription}are definitions we may use 
\begin{table}[htbp]
  \caption{Baseball Batting Statistics}
  \label{tab:discription} 
  \centering
  \begin{tabular}{|l|l|}
     \hline
     \textbf{Variable} & \textbf{Description}\\
     \hline
     $AB$ & At bats\\
     $AVG$ & Batting average\\
     $H$ & Hits\\
     $K$ & Strikeouts\\
     $HR$ & Home Run\\
     $BABIP$ & Batting Average on Balls in Play\\
     $SF$ & Sacrifice flies\\
    \hline
  \end{tabular}
\end{table}
